\section{Collaborators \& Other Affiliations Information}

\cut{
(iii) Collaborators & Other Affiliations Information (Single Copy Document) (See Chapter II.D.1 for additional information on Single Copy Documents.)
The following information regarding collaborators and other affiliations (COA) must be separately provided for each individual identified as senior personnel on the project. The COA information must be provided through use of the COA template. The information in the tables is not required to be sorted, alphabetically or otherwise. Refer to the frequently asked questions on the COA template page for additional information.

There are five separate categories of information which correspond to the five tables in the COA template:

COA template Table 1:

List the individual’s last name, first name, middle initial, and organizational affiliation in the last 12 months.

COA template Table 2:

List names as last name, first name, middle initial, for whom a personal, family, or business relationship would otherwise preclude their service as a reviewer. In the “Type of Relationship” column please specify the personal, family, or business relationship involved.

COA template Table 3:

List names as last name, first name, middle initial, and provide organizational affiliations, if known, for the following:

The individual’s Ph.D. advisors; and
All of the individual’s Ph.D. thesis advisees.
COA template Table 4:

List names as last name, first name, middle initial, and provide organizational affiliations, if known, for the following:

Co-authors on any book, article, report, abstract or paper with collaboration in the last 48 months (publication date may be later); and
Collaborators on projects, such as funded awards, graduate research, or others in the last 48 months.
COA template Table 5:

List editorial board, editor-in chief, and co-editors with whom the individual interacts. An editor-in-chief must list the entire editorial board.

Editorial Board:[36] List name(s) of editor-in-chief and journal in the past 24 months; and
Other co-Editors of journal or collections with whom the individual has directly interacted in the last 24 months.
The template has been developed to be fillable, however, the content and format requirements must not be altered by the user. When completing the template, do not change the column sizes or the font type. The instructions at the top of the template may be deleted, and rows may be inserted as needed to provide additional names[37].

This information is used to manage reviewer selection. See Exhibit II-2 for additional information on potential reviewer conflicts.


}

