\documentclass[11pt]{article}

\usepackage{fullpage}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{bigstrut}
\usepackage{tabularx}
\pagenumbering{gobble}

\begin{document}
\centerline{\noindent{\large{\textbf{Project Roles and Responsibilities}}}}

\begin{tabularx}{\textwidth}{llllX}
\toprule
Name & Role & Year &  Months & Responsibilities \\\midrule
\multicolumn{5}{c}{\textbf{Northern Arizona University}} \\\midrule
\multirow{3}{*}{Alex Groce} & \multirow{3}{*}{PI} & 1  & 1 & Supervise project startup, work on source-level transformations and custom mutators \\
                            &                     & 2  & 1 & Supervise project direction, lead outreach, work on source-level transformations and custom mutators \\
                            &                     & 3  & 1 & Supervise project completion and finalization, lead outreach, work on source-level transformations and custom mutators \\\midrule
 \multicolumn{5}{c}{\textbf{Carnegie Mellon University}} \\\midrule
 \multirow{3}{*}{Claire Le Goues} & \multirow{3}{*}{PI} & 1  &  0.5 & Supervise CMU team, advise student on source-level transformation for meta-fuzzing \\
                                  &                     & 2  &  0.75 &Supervise CMU team, advise student on source-level transformation for custom mutators, workshop planning  \\
                                  &                     & 3  &  0.75 & Supervise CMU team, advise student on domain specific fuzzing, workshop planning and execution  \\
 \multirow{3}{*}{Rohan Padhye}    & \multirow{3}{*}{co-PI} & 1 & 0.5 & Co-advise student, workshop execution   \\
                                  &                     & 2  &  0.5  & Co-advise student, workshop execution  \\
                                  &                     & 3  &  0.5 &  Co-advise student, workshop execution \\\bottomrule
% \end{tabularx}

% \centerline{\noindent{{\emph{Table continues...}}}}

% \begin{tabularx}{\textwidth}{llllX}
% \toprule
Name & Role & Year &  Months & Responsibilities \\\midrule
\multicolumn{5}{c}{\textbf{University of Virgninia}} \\\midrule
\multirow{3}{*}{Jack W. Davidson}& \multirow{3}{*}{PI} & 1  & 1 & Supervise UVA team, coordinate public workshop development with development. \\
                                 &                     & 2  & 1 &  Supervise UVA team, workshop coordination and meta-fuzzing promotion.\\
                                 &                     & 3  & 1 &  Supervise UVA team, develop education materials for university classroom. \\
\multirow{3}{*}{Jason D. Hiser}  & \multirow{3}{*}{\parbox{1.75cm}{Senior \\ Personnel}} & 1 & 2   &  Meta-fuzzing backend API integration and development. \\
                                 &                     & 2  & 2 & Binary transformation for meta-fuzzing. \\
                                 &                     & 3  & 2 & Meta-fuzzing coordination experiments at scale. \\\midrule
\multirow{3}{*}{Anh Nguyen-Tuong}& \multirow{3}{*}{\parbox{1.75cm}{Senior \\ Personnel}} & 1 & 2  &  Workshop development \& presentations. \\
                                 &                     & 2  & 2 & Meta-fuzzing training material development. \\
                                 &                     & 3  & 2 &  Community support/debugging for meta-fuzzing end users. \\\bottomrule
\end{tabularx}

\end{document}